\thetitle

### 2022-04-26 paper/paper.tex
move variable elimination technique to preliminaries section; revise nestedness proof and associated algorithm with according references; corresp translations; submodularity proof and notes on previous algorithms; slight changes to intro and conclusion reflecting submodularity

% Language selector
\newif\ifen
\entrue% Change to false to export Korean

@@

\ifen
From a methodological standpoint, as Fu (2014) remarked, college application represents a somewhat subtle asset allocation problem. In computational finance, traditional portfolio optimization models weigh the sum of expected profit across all assets against a risk term, yielding a concave maximization problem with linear constraints (Markowitz 1952; Meucci 2005). But college applicants maximize the expected value of their \emph{best} asset: If a student is admitted to her $j$th choice, then she is indifferent as to whether she gets into her $(j+1)$th choice. As a result, the valuation function that students maximize is \emph{convex} in the expected utility associated with individual applications. Risk management is implicit in the college application problem because, in a typical admissions market, college preferability is negatively correlated with competitiveness. That is, students negotiate a tradeoff between attractive, selective “reach schools” and less preferable “safety schools” where admission is a safer bet (Jeon 2015). Finally, the combinatorial nature of the college application problem makes it difficult to solve using the gradient-based techniques used in continuous portfolio optimization. Fu estimated her equilibrium model (which considers application as a \emph{cost} rather than a constraint) by clustering the schools so that $m=8$, a scale at which enumeration is tractable. We pursue a more general solution.
\else
방법론적인 관점에서 보면, Fu (2014)가 주장한 바처럼 대학 지원 전략은 약간 미묘한 자산 배분 문제이다. 재정학 분야에서 고전적 포트폴리오 최적화 모형은 전체 자산에 대한 기대 총이익에서 위험회피 항을 뺌으로 선형식으로 제약된 오목 최대화 문제를 이룬다 (Markowitz 1952; Meucci 2005). 그러나 대학 지원자는 가치가 제일 높은 단일 자산의 기대 가치를 최대화하고자 한다. 어떤 학생이 자신이 $j$번째로 선호하는 학교에 합격하면 $(j+1)$번째 학교의 합격 여부는 무관한 상황이 된다. 이는 학생이 최대화하려는 함수를 각 지원 발송의 기대 효용에 대해 오목이 아닌 볼록 함수로 만든다. 또한 입학 시장에서는 전형적으로 대학의 효용과 합격 확률이 서로 반비례하므로 대학 지원 문제는 위험 관리를 포함하게 된다. 특히 선호도가 높으며 붙기 어려운 “상향” 지원 학교(reach school)와 선호도가 낮으며 붙기 쉬운 “안정” 지원 학교(safety school) 사이의 균형을 고려해야 한다 (전민희 2015). 마지막, 대학 지원의 조합적인 본성으로 인해 연속적인 포트폴리오 최적화 문제에서 흔히 사용하는 기울기 해법으로는 풀기가 어렵다. Fu는 지원 비용을 제약 조건 대신 목적함수의 한 항으로 모형화했으며, 균형 모형의 모수를 추정하기 위해 $m=8$이 되도록 학교들의 클러스터를 먼저 구성했다. 이는 열거법을 통해 문 쉽게 풀 수 있는 규모이지만 본 연구는 더 일반적인 $m$에 대한 해법을 추구한다.
\fi

@@

\ifen
For certain classes of optimization problems, such as maximizing a submodular set function over a cardinality constraint, a greedy algorithm is known to be a good approximate solution and exact under certain additional assumptions (Fisher et al. 1978). For other problems, notably the binary knapsack problem, the most intuitive greedy algorithm can be made to perform arbitrarily poorly (Vazirani 2001). We show results for the college application problem that mirror those for knapsack: In the special case where each $g_j = 1$, the optimal portfolio satisfy a nestedness property that is equivalent to the validity of the greedy algorithm. This case mirrors the centralized college application process in Korea, where there is no application fee, but students are allowed to apply to only three schools during the main admissions cycle. Unfortunately, the nestedness property does not hold in the general case, nor does the greedy algorithm offer any performance guarantee. Instead, we offer a branch-and-bound routine, a pseudopolynomial-time algorithm that is tractable for typical college market instances, and a fully polynomial-time approximation scheme (FPTAS).
\else
탐욕 알고리즘이 좋은 근사해거나 정확한 알고리즘이 되는 최적화 모형들이 알려져 있다. 집합 크기 제약 하에서 하위 모듈 집합 함수(submodular set function)를 최대화하는 문제가 대표적인 예다 (Fisher 외 1978). 반면에 이진 배낭 문제 같은 경우에서는 가장 직관적인 탐욕 알고리즘이 최적과 거리가 먼 해를 출력하는 예를 만들 수 있다 (Vazirani 2001). 대학 지원 문제와 배낭 문제가 서로 매우 유사함을 보인다. 모든 $g_j=1$인 특수한 경우에서, 최적 포트폴리오가 탐욕 알고리즘의 타당성과 동등한 포함 사슬 관계를 만족하는 것을 증명한다. 이 경우는 지원 비용이 없으며 정시 모집 기간에 학교 3개에만 지원할 수 있는 한국 입학 과정과 같다. 그러나 일반적인 경우에서 포함 사슬 관계가 성립하지 않을뿐더러 탐욕 알고리즘이 어떤 근사 계수를 보장할 수 없을 보일 수 있다. 대신 분지한계법, 전형적인 입학 시장 인스턴스에 대해 효율적인 의사 다항 시간 동적 계획, 그리고 완전 다항 시간 근사 해법(fully polynomial-time approximation scheme, FPTAS)을 제시한다.
\fi

% following sentence buries the lede
% decide how to handle FPTAS abbrev
Although our research employs more elementary techniques, we remark that the objective function of \ref{headlineproblem} is a nondecreasing submodular function, and our approximation results are tighter than those that arise in the generic case. Fisher et al.'s result (1978), for example, implies that the greedy algorithm is asymptotically $(1 - 1/e)$-optimal for the $g_1 = 1$ case of the college application problem, whereas we show that the same algorithm is exact. Using relaxation techniques, a nearly equivalent approximation ratio is achievable when maximizing a submodular set function over knapsack constraints or matroids (Calinescu et al. 2011; Kulik et al. 2013). In the college application problem, the existence of the FPTAS supersedes these results.

\ifen \subsection{Structure of this paper} \else \subsection{본 논문의 구성}\fi
\ifen Section \ref{preliminaries} introduces some additional notation and assumptions that can be imposed without loss of generality. 
\else \ref{preliminaries}절은 표기법과 일반성을 제한하지 않는 편의적 가정을 제시한다.\fi

@@

\ifen
In Section \ref{numericalexperiments}, we present the results of computational experiments that confirm the validity and time complexity results established in the previous two sections. % more

A brief conclusion follows.
\else
\ref{numericalexperiments}절에서 위에서 도출한 타당성과 계산 복잡성을 확인하는 계산 실험 결과를 정리한다.

그리고 간단한 결론을 제시한다.
\fi

@@

@@

%% Work text from nestedness proof into here, or probably better to just rewrite

%Now, we present a variable-elimination technique that will prove useful throughout the paper. Suppose that the student has already resolved to apply to $c_k$, and the remainder of her decision consists of determining which \emph{other} schools to apply to. We can write her total application portfolio as $\mathcal{X} = \mathcal{Y} \cup \{k\}$, and we are interested in devising a function $w(\mathcal{Y})$ that orders portfolios according to how well they ``complement'' the singleton portfolio $\{k\}$.  To construct $w(\mathcal{Y})$ .. %this part is like the proof
%
%\begin{proposition}[\ifen Eliminate $c_k$\else $c_k$ 소거\fi]
%\ifen For $\mathcal{X} \subseteq \mathcal{C} \setminus \{k\}$, $v(\mathcal{X}\cup\{k\}; t)  = v(\mathcal{X}; \bar t) + f_k t_k$, where
%\else $\mathcal{X} \subseteq \mathcal{C} \setminus \{k\}$에 대해, $v(\mathcal{X}\cup\{k\}; t)  = v(\mathcal{X}; \bar t) + f_k t_k$이다. 단,\fi
%\begin{align}\label{howtotransformfj}
%\bar t_j = 
%\begin{cases}
%(1 - f_k) t_j, \quad & t_j \leq t_k \\
%t_j - f_k t_k, \quad& t_j > t_k.
%\end{cases}
%\end{align}
%\end{proposition}%
% It is easy to verify that this is the composition ...

%% Prove submodularity

@@

\ifen Now suppose that $k \in \mathcal{X}_h$. We can write $\mathcal{X}_h = \mathcal{Y}_{h-1} \cup \{k\}$, where $ \mathcal{Y}_{h-1}$ is some portfolio of size $h-1$. It suffices to show that $ \mathcal{Y}_{h-1} \subset \mathcal{Y}_h$. By definition, $\mathcal{Y}_{h-1}$ (respectively, $\mathcal{Y}_{h}$) maximizes the function $v(\mathcal{Y}\cup\{k\})$ over portfolios of size $h-1$ (respectively, $h$) that do not include $k$. That is, $\mathcal{Y}_{h-1}$ and $\mathcal{Y}_h$ are the optimal \emph{complements} to the singleton portfolio $\{k\}$.
\else 이제 $k \in \mathcal{X}_h$인 경우를 고려하자. 그러면 크기 $h-1$인 어떤 포트폴리오 $\mathcal{Y}_{h-1}$에 대해 $\mathcal{X}_h = \mathcal{Y}_{h-1} \cup \{k\}$으로 표현할 수 있다. $\mathcal{Y}_{h-1} \subset \mathcal{Y}_h$임을 보이면 충분하다. 정의에 따라 $\mathcal{Y}_{h-1}$ ($\mathcal{Y}_{h}$)는 크기가 $h-1$ ($h$)인 포트폴리오 중에 함수 $v(\mathcal{Y}\cup\{k\})$를 최대화한다. 다시 말해 $\mathcal{Y}_{h-1}$과 $\mathcal{Y}_h$는 각각 단일 원소 포트폴리오 $\{k\}$와 최적으로 `보완적인' 학교 집합이다. \fi

>>>>

% Language selector
\newif\ifen
\enfalse% Change to false to export Korean

@@

\ifen
From a methodological standpoint, as Fu (2014) remarked, college application represents a somewhat subtle asset allocation problem. In computational finance, traditional portfolio optimization models weigh the sum of expected profit across all assets against a risk term, yielding a concave maximization problem with linear constraints (Markowitz 1952; Meucci 2005). But college applicants maximize the expected value of their \emph{best} asset: If a student is admitted to her $j$th choice, then she is indifferent as to whether she gets into her $(j+1)$th choice. As a result, the valuation function that students maximize is \emph{convex} in the expected utility associated with individual applications. Risk management is implicit in the college application problem because, in a typical admissions market, college preferability is negatively correlated with competitiveness. That is, students negotiate a tradeoff between attractive, selective “reach schools” and less preferable “safety schools” where admission is a safer bet (Jeon 2015). Finally, the combinatorial nature of the college application problem makes it difficult to solve using the gradient-based techniques used in continuous portfolio optimization. Fu estimated her equilibrium model (which considers application as a \emph{cost} rather than a constraint) by clustering the schools so that $m=8$, a scale at which enumeration is tractable. We pursue a more general solution.
\else
방법론적인 관점에서 보면, Fu (2014)가 주장한 바처럼 대학 지원 전략은 약간 미묘한 자산 배분 문제이다. 재정학 분야에서 고전적 포트폴리오 최적화 모형은 전체 자산에 대한 기대 총이익에서 위험회피 항을 뺌으로 선형식으로 제약된 오목 최대화 문제를 이룬다 (Markowitz 1952; Meucci 2005). 그러나 대학 지원자는 가치가 제일 높은 단일 자산의 기대 가치를 최대화하고자 한다. 어떤 학생이 자신이 $j$번째로 선호하는 학교에 합격하면 $(j+1)$번째 학교의 합격 여부는 무관한 상황이 된다. 이는 학생이 최대화하려는 함수를 각 지원 발송의 기대 효용에 대해 오목이 아닌 볼록 함수로 만든다. 또한 입학 시장에서는 전형적으로 대학의 효용과 합격 확률이 서로 반비례하므로 대학 지원 문제는 위험 관리를 포함하게 된다. 특히 선호도가 높으며 붙기 어려운 “상향” 지원 학교(reach school)와 선호도가 낮으며 붙기 쉬운 “안정” 지원 학교(safety school) 사이의 균형을 고려해야 한다 (전민희 2015). 마지막, 대학 지원의 조합적인 본질로 인해 연속적인 포트폴리오 최적화 문제에서 흔히 사용하는 기울기 해법으로는 풀기가 어렵다. Fu는 지원 비용을 제약 조건 대신 목적함수의 한 항으로 모형화했으며, 균형 모형의 모수를 추정하기 위해 $m=8$이 되도록 학교들의 클러스터를 먼저 구성했다. 이는 열거법을 통해 문 쉽게 풀 수 있는 규모이지만 본 연구는 더 일반적인 $m$에 대한 해법을 추구한다.
\fi

@@

\ifen
For certain classes of optimization problems, such as maximizing a submodular set function over a cardinality constraint, a greedy algorithm is known to be a good approximate solution and exact under certain additional assumptions (Fisher et al. 1978). For other problems, notably the binary knapsack problem, the most intuitive greedy algorithm can be made to perform arbitrarily poorly (Vazirani 2001). We show results for the college application problem that mirror those for knapsack: In the special case where each $g_j = 1$, the optimal portfolio satisfy a nestedness property that is equivalent to the validity of the greedy algorithm. This case mirrors the centralized college application process in Korea, where there is no application fee, but students are allowed to apply to only three schools during the main admissions cycle. Unfortunately, the nestedness property does not hold in the general case, nor does the greedy algorithm offer any performance guarantee. Instead, we offer a branch-and-bound routine, a pseudopolynomial-time algorithm that is tractable for typical college market instances, and a fully polynomial-time approximation scheme (FPTAS).
\else
탐욕 알고리즘이 좋은 근사해거나 정확한 알고리즘이 되는 최적화 모형들이 알려져 있다. 집합 크기 제약 하에서 submodular한 집합 함수를 최대화하는 문제가 대표적인 예다 (Fisher 외 1978). 반면에 이진 배낭 문제 같은 경우에서는 가장 직관적인 탐욕 알고리즘이 최적과 거리가 먼 해를 출력하는 예를 만들 수 있다 (Vazirani 2001). 대학 지원 문제와 배낭 문제가 서로 매우 유사함을 보인다. 모든 $g_j=1$인 특수한 경우에서, 최적 포트폴리오가 탐욕 알고리즘의 타당성과 동등한 포함 사슬 관계를 만족하는 것을 증명한다. 이 경우는 지원 비용이 없으며 정시 모집 기간에 학교 3개에만 지원할 수 있는 한국 입학 과정과 같다. 그러나 일반적인 경우에서 포함 사슬 관계가 성립하지 않을뿐더러 탐욕 알고리즘이 어떤 근사 계수를 보장할 수 없을 보일 수 있다. 대신 분지한계법, 전형적인 입학 시장 인스턴스에 대해 효율적인 의사 다항 시간 동적 계획, 그리고 완전 다항 시간 근사 해법(fully polynomial-time approximation scheme, FPTAS)을 제시한다.
\fi

% following sentence buries the lede（
\ifen
Finally, we remark that the objective function of \ref{headlineproblem} is a nondecreasing submodular function. However, our research employs more elementary analytical techniques, and our approximation results are tighter than those associated with generic submodular maximization algorithms. For example, a well-known result of Fisher et al. (1978) implies that the greedy algorithm is asymptotically $(1 - 1/e)$-optimal for the $g_j = 1$ case of the college application problem, whereas we show that the same algorithm is exact. When maximizing a submodular set function over knapsack constraints or matroids, a nearly equivalent approximation ratio is achievable using relaxation techniques (Calinescu et al. 2011; Kulik et al. 2013). But in the general case of the college application problem, the existence of the FPTAS supersedes these results.
\else
마지막으로, \ref{headlineproblem}의 목적함수는 submodular하며 단조 증가하는 함수이다. 그런데, 본 연구는 더 기초적인 분석 기술을 이용하며, 일반적인 submodular 최대화 알고리즘보다 좋은 근사 계수를 얻게 된다. 예를 들어 Fisher 외 (1978)의 잘 알려진 결과에 따라, 대학 지원 문제의 $g_j = 1$인 경우에서 탐욕 해법의 점근적 근사 계수가 $(1 - 1/e)$이 되며, 본 논문에서 같은 해법이 정확함을 보인다. 다중 배낭 제약식 혹은 매트로이드 위에서 submodular 집합 함수를 최대하는 문제에서, 완화 기술을 활용하면 거의 동등한 근사 계수를 이뤄 낼 수 있다 (Calinescu et al. 2011; Kulik et al. 2013). 그러나 일반적인 대학 지원 문제에서, FPTAS의 존재성은 그 결과를 대체한다.
\fi

\ifen \subsection{Structure of this paper} \else \subsection{본 논문의 구성}\fi
\ifen Section \ref{preliminaries} introduces some additional notation and assumptions that can be imposed without loss of generality. We also introduce a useful variable-elimination technique and prove that the objective function is submodular.
\else \ref{preliminaries}절은 표기법과 일반성을 제한하지 않는 편의적 가정을 제시한다. 유용한 변수 소거 기술도 제시하고 목적함수가 submodularity함을 증명한다.\fi

@@

\ifen
In Section \ref{numericalexperiments}, we present the results of computational experiments that confirm the validity and time complexity results established in the previous two sections. We also investigate the empirical accuracy of the simulated-annealing heuristic.

In the conclusion, we identify possible improvements to our solution algorithms and introduce a few extensions of the model that capture the features of real-world admissions processes.
\else
\ref{numericalexperiments}절에서 위에서 도출한 타당성과 계산 복잡성을 확인하는 계산 실험 결과를 정리한다. 모의 담금질 휴리스틱의 정확도도 탐구한다.

결론에서, 해법을 개선할 수 있는 요소를 언급하고, 실제 지원 과정의 특징을 묘사하도록 원래 모형을 확장할 수 있는 기술 몇 가지 소개한다.
\fi

@@

\ifen \subsection{Refining the objective function} \else \subsection{목적함수의 정제} \fi

@@

\subsection{A variable-elimination technique}
\ifen
Now, we present a variable-elimination technique that will prove useful throughout the paper.\footnote{We thank Yim Seho for pointing out this useful transformation.} Suppose that the student has already resolved to apply to $c_k$, and the remainder of her decision consists of determining which \emph{other} schools to apply to. Writing her total application portfolio as $\mathcal{X} = \mathcal{Y} \cup \{k\}$, we devise a function $w(\mathcal{Y})$ that orders portfolios according to how well they ``complement'' the singleton portfolio $\{k\}$. Specifically, the difference between $v(\mathcal{Y} \cup\{k\})$ and $w(\mathcal{Y})$ is the constant $f_k t_k$.
\else
본 항에서 남은 논문에서 활용되는 변수 소거 기술을 소개한다.\footnote{이 유용한 변환을 발견한 임세호에게 감사를 표한다.} 학생이 $c_k$에 지원하기로 결심하고, 남은 결정 공간은 어떤 다른 학교에 지원하는 것으로 제한된다고 하자. 전체 지원 포트폴리오를 $\mathcal{X} = \mathcal{Y} \cup \{k\}$일 때, $\mathcal{Y} \subseteq \mathcal{C} \setminus \{k\}$인 포트폴리오와 $\{k\}$ 사이의 \mbox{`보완성'을} 평가하는 함수 $w(\mathcal{Y})$를 도출할 수 있다. 단, $v(\mathcal{Y} \cup\{k\})$와 $w(\mathcal{Y})$ 사이에서 $f_k t_k$ 같은 상수 차이가 발생한다.
\fi

\ifen
To construct $w(\mathcal{Y})$, let $\tilde t_j$ denote the expected utility the student receives from school $c_j$ \emph{given} that she has been admitted to $c_j$ and applied to $c_k$. For $j < k$ (including $j = 0$), this is $\tilde t_j = (1- f_k) t_j + f_k t_k$; for $j > k $, this is $\tilde t_j = t_j$. This means that 
\begin{equation}\label{Vyastildet}
v(\mathcal{Y}\cup\{k\}) = \sum_{j \in \{0\} \cup \mathcal{Y}} \tilde t_j p_j(\mathcal{Y}).\end{equation}
The transformation to $\tilde t$ does not change the order of the $t_j$-values. Therefore, the expression on the right side of \eqref{Vyastildet} is itself a portfolio valuation function. In the corresponding market, $t$ is replaced by $\tilde t$ and $\mathcal{C}$ is replaced by $\mathcal{C}\setminus\{k\}$. To restore our convention that $t_0 = 0$, we obtain $w(\mathcal{Y})$ by taking $\bar t_j = \tilde t_j - \tilde t_0$ for all $j \neq k$ and letting
\begin{equation}  \label{wYvXminusconst}
w(\mathcal{Y})
= \sum_{j \in \{0\} \cup \mathcal{Y}} \bar t_j p_j(\mathcal{Y})
= \sum_{j \in \{0\} \cup \mathcal{Y}} \tilde t_j p_j(\mathcal{Y})- \tilde t_0
= v(\mathcal{Y}\cup\{k\}) -  f_k t_k \end{equation}
where the second equality follows from Theorem \ref{assumetzerozero}. The validity of this transformation is summarized in the following theorem, where we write $v(\mathcal{X}; \bar t)$ instead of $w(\mathcal{Y})$ to emphasize that $w(\mathcal{Y})$ is, in form, a portfolio valuation function. 
\else
$w(\mathcal{Y})$를 구성하기 위해, 알마가 $c_j$에 합격한 상황에서 $c_k$에 지원했을 때 $c_j$에서 받는 조건부 기대 효용을 $\tilde t_j$라고 하자. $j = 0$을 포함한 $j < k$에 대해 이값은 $\tilde t_j = t_j (1- f_k) + t_k f_k$이며, $j > k $에 대해 $\tilde t_j = t_j$임을 알 수 있다. 따라서 
\begin{equation}\label{Vyastildet}
v(\mathcal{Y}\cup\{k\}) = \sum_{j \in \{0\} \cup \mathcal{Y}} \tilde t_j p_j(\mathcal{Y}).\end{equation}
$\tilde t$로 변환하면 $t_j$의 순서가 변하지 않기 때문에 \eqref{Vyastildet}의 우변 그 자체가 포트폴리오 가치 함수이다. $t$를 $\tilde t$로, $\mathcal{C}$를 $\mathcal{C}\setminus \{k\}$로 대체하면 대응하는 시장이 된다. 그다음에 $t_0 = 0$이 되도록 $\bar t_j = \tilde t_j - \tilde t_0$으로 정의하고 $w(\mathcal{Y})$를 다음처럼 얻을 수 있다. 
\begin{equation}  \label{wYvXminusconst}
w(\mathcal{Y})
= \sum_{j \in \{0\} \cup \mathcal{Y}} \bar t_j p_j(\mathcal{Y})
= \sum_{j \in \{0\} \cup \mathcal{Y}} \tilde t_j p_j(\mathcal{Y})- \tilde t_0
= v(\mathcal{Y}\cup\{k\}) -  f_k t_k \end{equation}
두 번째 등호는 정리 \ref{assumetzerozero}에 따라 성립한다. 다음 정리는 이 변환의 타당성을 의미한다. 단, $w(\mathcal{Y})$가 포트폴리오 가치 함수 형태를 가지는 것을 강조하기 위해 $w(\mathcal{Y})$ 대신 $v(\mathcal{X}; \bar t)$처럼 표기한다.
\fi

\begin{theorem}[\ifen Eliminate $c_k$\else $c_k$ 소거 기술\fi] \label{eliminationtheorem}
\ifen For $\mathcal{X} \subseteq \mathcal{C} \setminus \{k\}$, $v(\mathcal{X}\cup\{k\}; t)  = v(\mathcal{X}; \bar t) + f_k t_k$, where
\else $\mathcal{X} \subseteq \mathcal{C} \setminus \{k\}$에 대해, $v(\mathcal{X}\cup\{k\}; t)  = v(\mathcal{X}; \bar t) + f_k t_k$이다. 단,\fi
\begin{align}\label{howtotransformtj}
\bar t_j = 
\begin{cases}
(1 - f_k) t_j, \quad & t_j \leq t_k \\
t_j - f_k t_k, \quad& t_j > t_k.
\end{cases}
\end{align}
\end{theorem}

\begin{proof}
\ifen It is easy to verify that \eqref{howtotransformtj} is the composition of the two transformations (from $t$ to $\tilde t$, and from $\tilde t$ to $\bar t$) discussed above.
\else \eqref{howtotransformtj}이(가) 위에서 논의한 2개의 변환($t$에서 $\tilde t$로, 그리고 $\tilde t$에서 $\bar t$로)의 합성임을 쉽게 확인할 수 있다. \fi
\end{proof}

\ifen
\noindent The transformation \eqref{howtotransformtj} can be applied iteratively to accommodate the case where the student has already resolved to apply to multiple schools.
\else
\noindent 학생이 다수의 학교에 지원하기로 결심한 경우를 반영하기 위해, \eqref{howtotransformtj}의 변화를 반복적으로 적용할 수 있다.
\fi

\ifen \subsection{Submodularity of the objective function} \else \subsection{목적함수의 submodularity} \fi
\ifen 
Now, we show that the portfolio valuation function is submodular. This result is primarily of taxonomical interest and may be safely skipped. Our solution algorithms for the college application problem are better than generic algorithms for submodular maximization, and we prove their validity using elementary analysis.
\else
목적함수가 submodular함을 보이자. 이 결과는 주로 분류학적인 흥미를 가지며 건너뛰어도 연속성에 지장을 주지 않는다. 일반적인 submodular 최대화 알고리즘보다 본 연구가 제시하는 대학 지원 최적화 해법이 더 좋으며, 기초적인 분석을 통해 그의 타당성을 증명한다.
\fi

\ifen
\begin{definition}[Submodular set function]
Given a ground set $\mathcal{C}$ and function $v : 2^{\mathcal{C}} \mapsto \mathbb{R}$, $v(\mathcal{X})$ is called a \emph{submodular set function} if and only if $v(\mathcal{X}) + v(\mathcal{Y}) \geq v(\mathcal{X}\cup\mathcal{Y}) + v(\mathcal{X}\cap\mathcal{Y})$
for all $\mathcal{X}, \mathcal{Y} \subseteq \mathcal{C}$. Furthermore, if $ v(\mathcal{X}\cup\{k\}) - v(\mathcal{X}) \geq 0$ for all $\mathcal{X} \subset \mathcal{C}$ and $k \in \mathcal{C} \setminus \mathcal{X}$, $v(\mathcal{X})$ is said to be a \emph{nondecreasing} submodular set function.
\end{definition}
\else
\begin{definition}[Submodular한 집합 함수]
고려 집합 $\mathcal{C}$ 그리고 함수 $v : 2^{\mathcal{C}} \mapsto \mathbb{R}$가 주어질 때, $v(\mathcal{X})$가 submodular한 집합 함수가 되는 필수충분 조건은, 모든 $\mathcal{X}, \mathcal{Y} \subseteq \mathcal{C}$에 대해 $v(\mathcal{X}) + v(\mathcal{Y}) \geq v(\mathcal{X}\cup\mathcal{Y}) + v(\mathcal{X}\cap\mathcal{Y})$이 성립하는 것이다. 또한 모든 $\mathcal{X} \subset \mathcal{C}$와 $k \in \mathcal{C} \setminus \mathcal{X}$에 대해 $v(\mathcal{X}\cup\{k\}) - v(\mathcal{X}) \geq 0$이면, $v(\mathcal{X})$가 단조 증가하는 submodular한 집합 함수라고 부른다.
\end{definition}
\fi

\ifen
\begin{theorem}
The college application portfolio valuation function
$v(\mathcal{X})$ % = \sum_{j\in\mathcal{X}} \Bigl( f_j t_j \prod_{\substack{i \in \mathcal{X}: \\ i > j}} (1 - f_{i}) \Bigr)\]
is a nondecreasing submodular set function.
\end{theorem}
\else
\begin{theorem}
대학 지원의 포트폴리오 가치 함수 $v(\mathcal{X})$는 submodular한 집합 함수이다.
\end{theorem}
\fi

\ifen
\begin{proof}
It is self-evident that $v(\mathcal{X})$ is nondecreasing. To establish its submodularity, we apply proposition 2.1.iii of Nemhauser and Wolsey (1978) and show that
\begin{equation}\label{nemhauseriii}
v(\mathcal{X} \cup \{j\}) - v(\mathcal{X}) \geq 
v(\mathcal{X} \cup \{j, k\}) - v(\mathcal{X} \cup \{k\})
\end{equation}
for $\mathcal{X} \subset \mathcal{C}$ and $j \neq k \in \mathcal{C} \setminus \mathcal{X}$. By repeatedly eliminating the schools in $\mathcal{X}$ according to \eqref{howtotransformtj}, we can obtain a portfolio valuation function $w(\mathcal{Y})$ with parameter $\bar t$ such that $w(\mathcal{Y}) = v(\mathcal{X} \cup \mathcal{Y}) + \text{const.}$ for any $\mathcal{Y} \subseteq \mathcal{C} \setminus \mathcal{X}$. Therefore, \eqref{nemhauseriii} is equivalent to
\begin{align}
& w(\{j\}) - w(\varnothing) \geq w(\{j, k\}) - w(\{k\}) \\
\iff \qquad &w(\{j\})  +  w(\{k\})  \geq w(\{j, k\})  \\
\iff \qquad &\operatorname{E}[\,\bar t_j Z_j\,] + \operatorname{E}[\,\bar t_k Z_k\,] 
\geq \operatorname{E}\bigl[\max\{ \bar t_j Z_j, \bar t_k Z_k \} \bigr]
\end{align}
which is plainly true. 
\end{proof}
\else
\begin{proof}
$v(\mathcal{X})$가 단조 증가하는 것은 자명하다. Submodularity를 보이기 위해, Nemhauser와 Wolsey (1978)의 제의 2.1.iii을 적용하여 모든 $\mathcal{X} \subset \mathcal{C}$ 그리고 $j \neq k \in \mathcal{C} \setminus \mathcal{X}$에 대해 다음이 성립함을 보이자.
\begin{equation}\label{nemhauseriii}
v(\mathcal{X} \cup \{j\}) - v(\mathcal{X}) \geq 
v(\mathcal{X} \cup \{j, k\}) - v(\mathcal{X} \cup \{k\})
\end{equation}
\eqref{howtotransformtj}에 따라 $\mathcal{X}$에 속한 학교를 반복적으로 소거하면 모수 $\bar t$로 갖춘 포트폴리오 함수 $w(\mathcal{Y})$를 얻을 수 있으며,  모든 $\mathcal{Y} \subseteq \mathcal{C} \setminus \mathcal{X}$에 대해 $w(\mathcal{Y}) = v(\mathcal{X} \cup \mathcal{Y}) + \text{const.}$가 성립한다. 따라서 \eqref{nemhauseriii}은(는) 다음 부등식과 동등하다.
\begin{align}
& w(\{j\}) - w(\varnothing) \geq w(\{j, k\}) - w(\{k\}) \\
\iff \qquad &w(\{j\})  +  w(\{k\})  \geq w(\{j, k\})  \\
\iff \qquad &\operatorname{E}[\,\bar t_j Z_j\,] + \operatorname{E}[\,\bar t_k Z_k\,] 
\geq \operatorname{E}\bigl[\max\{ \bar t_j Z_j, \bar t_k Z_k \} \bigr]
\end{align}
마지막 부등식은 분명히 참이다.
\end{proof}
\fi

@@

\ifen Now suppose that $k \in \mathcal{X}_h$. We can write $\mathcal{X}_h = \mathcal{Y}_{h-1} \cup \{k\}$, where $ \mathcal{Y}_{h-1}$ is some portfolio of size $h-1$. It suffices to show that $ \mathcal{Y}_{h-1} \subset \mathcal{Y}_h$. By definition, $\mathcal{Y}_{h-1}$ (respectively, $\mathcal{Y}_{h}$) maximizes the function $v(\mathcal{Y}\cup\{k\})$ over portfolios of size $h-1$ (respectively, $h$) that do not include $k$. That is, $\mathcal{Y}_{h-1}$ and $\mathcal{Y}_h$ are the optimal complements to the singleton portfolio $\{k\}$.

Applying Theorem \ref{eliminationtheorem}, we eliminate $c_k$, transform the remaining $t_j$-values to $\bar t_j$ according to \eqref{howtotransformtj}, and obtain a function $w(\mathcal{Y}) = v(\mathcal{Y} \cup \{k\}) - f_k t_k$ that grades portfolios $\mathcal{Y} \subseteq \mathcal{C} \setminus \{k\}$ according to how well they complement $\{k\}$. Since $w(\mathcal{Y})$ is itself a portfolio valuation funtion and $\bar t_0 = 0$, the inductive hypothesis implies that $\mathcal{Y}_{h-1} \subset \mathcal{Y}_h$, which completes the proof.

\else 이제 $k \in \mathcal{X}_h$인 경우를 고려하자. 그러면 크기 $h-1$인 어떤 포트폴리오 $\mathcal{Y}_{h-1}$에 대해 $\mathcal{X}_h = \mathcal{Y}_{h-1} \cup \{k\}$으로 표현할 수 있다. $\mathcal{Y}_{h-1} \subset \mathcal{Y}_h$임을 보이면 충분하다. 정의에 따라 $\mathcal{Y}_{h-1}$ ($\mathcal{Y}_{h}$)는 크기가 $h-1$ ($h$)인 포트폴리오 중에 함수 $v(\mathcal{Y}\cup\{k\})$를 최대화한다. 다시 말해 $\mathcal{Y}_{h-1}$과 $\mathcal{Y}_h$는 각각 단일 원소 포트폴리오 $\{k\}$와 최적으로 보완적인 학교 집합이다.

정리 \ref{eliminationtheorem}을(를) 적용하여 $c_k$를 소거하고 남은 $t_j$-값을 \eqref{howtotransformtj}에 따라 $\bar t_j$로 변환한다. 그러면 $\mathcal{Y} \subseteq \mathcal{C} \setminus \{k\}$인 포트폴리오와 $\{k\}$ 사이의 보완성을 평가하는 함수 $w(\mathcal{Y})$를 얻는다. $w(\mathcal{Y})$ 그 자체가 포트폴리오 가치 함수이며 $\bar t_0 = 0$이므로, 귀납법 가설에 따라 $\mathcal{Y}_{h-1} \subset \mathcal{Y}_h$이고 증명이 완성된다.
\fi
\end{proof}
